\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-05-24 eg6-letters/NIM/EG6_RTPC_NIM.tex
editing the figures for the nim paper
update figure 8 in the NIM
update figure 7 in the NIM paper

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.3]{fig/TDC_profile.png}
   \caption[]{Time profile of the collected hits in one experimental run.  } 
   \label{fig:TDC_profile}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.36]{fig/RunNumber_61551_TDCmax_Zslice.png}
\caption{Time profile distribution for the collected hits in one experimental 
run. } \label{fig:RunNumber_61551_TDCmax_Zslice}
\end{figure}

@@

\begin{figure}[tb]
\hspace*{-1.8cm}
\includegraphics[scale=0.26]{fig/Drift_run_number_1.png}
\caption{$T_{Nbmax/2}$ versus the experimental run numbers (time).  } 
\label{fig:Drift_run_number_1}
\end{figure}

>>>>

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.42]{fig_2017/hits_time_profile.pdf}
   \caption[]{Time profile of the collected hits in one experimental run.  } 
   \label{fig:TDC_profile}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.42]{fig_2017/RunNumber_61452_TDCmax_Zslice.pdf}
\caption{Time profile distribution for the collected hits in one experimental 
run. } \label{fig:RunNumber_61551_TDCmax_Zslice}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.45]{fig_2017/Drift_run_number.pdf}
\caption{$T_{Nbmax/2}$ versus the experimental run numbers (time).  } 
\label{fig:Drift_run_number_1}
\end{figure}
